Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-05-20 cover_letter/letterhead.tex
Andy pre-submission edits
final submission edits

%\documentclass[11pt,a4paper,draft]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc) 
\documentclass[11pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc) 
\usepackage{letterbib}
\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
\usepackage{fancyhdr}
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage[sort&compress,numbers,super]{natbib}
\usepackage{caption}
\usepackage{newfloat}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{soul}
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{calligra}
\usepackage{fp}
\FPset\marginWidth{0.7}	% margin width (all sides) in inches
\usepackage[margin=\marginWidth in]{geometry}
\usepackage{marginfix}
\usepackage[colorlinks=true,
            linkcolor=blue,
            urlcolor=blue,
            citecolor=blue]{hyperref}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter

@@

%more new commands and definitions
\newcommand*{\rood}[1]{\textcolor{red}{#1}}
\newcommand*{\blauw}[1]{\textcolor{blue}{#1}}
\newcommand*{\groen}[1]{\textcolor{green}{#1}}
\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
\newcommand{\scripty}[1]{\ensuremath{\mathcalligra{#1}}}

@@

\def\Who{Andrew L. Ferguson} % Your name
\def\What{, PhD} % Your title
\def\Where{Pritzker School of Molecular Engineering\\University of Chicago} % Your department/institution
\def\department{Pritzker School of Molecular Engineering}
\def\institution{University of Chicago}
\def\Address{5640 South Ellis Avenue} % Your address
\def\CityZip{Chicago, IL 60637} % Your city, zip code, country, etc
\def\Email{e:~\url{andrewferguson@uchicago.edu}} % Your email address
\def\TEL{p:~(773)~702-5950} % Your phone number
\def\URL{w:~\url{http://andrewferguson.uchicago.edu}} % Your URL
\def\titleone{Associate Professor}

@@

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
%\hspace*{\longindentation} % Move the signature right
%\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.0in
\includegraphics[width=0.25\textwidth]{signature_720}
%\vskip 0.65in % Whitespace between the signature text and your name
\\
\noindent
\fromsig
\vskip -0.05in
\titleone\\
\department\\
\institution\\
\vskip -0.1in
\noindent cc: M.S.~Jones, B.~Ashwood, A.~Tokmakoff
}

@@

% what we did in this paper
\textbf{Key Results.}  In this work, we establish new understanding of the sequence-dependent hybridization/dehybridization kinetics and mechanism within a family of self-complementary pairs of 10-mer DNA oligomers by integrating coarse-grained molecular simulation, machine learning, data-driven inference of long-time kinetic models, and experimental temperature-jump infrared spectroscopy. We conducted more than 1 ms of coarse-grained molecular dynamics simulations and employed deep learning techniques to construct high-resolution Markov state models as predictive and interpretable models of the sequence dependent dynamics. Our results reveal that the specific placement of interrupting G:C pairs within an otherwise repetitive AT sequence can have a profound impact on the kinetic pathways and mechanisms for association and dissociation of the DNA duplex.

@@

% fit for the journal
\textbf{Scope.}  This work fits within the scope of \textit{The Journal of the American Chemical Society} in that it reports new fundamental physical chemical understanding of the molecular pathways and mechanisms of sequence-dependent DNA hybridization/dehybridization pathways. These sequence-dependent mechanisms are of both fundamental interest in biophysical and biochemical processes and of increasing importance in burgeoning DNA nanotechnology applications reliant on quantitative understanding of the sequence-dependent kinetic pathways and rates.

@@

We look forward to hearing from you.

>>>>

%\documentclass[11pt,a4paper,draft]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc) 
\documentclass[11pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc) 
\usepackage{letterbib}
\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
\usepackage{fancyhdr}
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage[sort&compress,numbers,super]{natbib}
%\usepackage{caption}
\usepackage{newfloat}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{soul}
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{calligra}
\usepackage{fp}
\FPset\marginWidth{0.7}	% margin width (all sides) in inches
\usepackage[margin=\marginWidth in]{geometry}
\usepackage{marginfix}
\usepackage[colorlinks=true,
            linkcolor=blue,
            urlcolor=blue,
            citecolor=blue]{hyperref}

% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter

@@

%more new commands and definitions
\newcommand*{\rood}[1]{\color{red}{#1}}
\newcommand*{\blauw}[1]{\color{blue}{#1}}
\newcommand*{\groen}[1]{\color{green}{#1}}
%\newcommand*{\rood}[1]{\textcolor{red}{#1}}
%\newcommand*{\blauw}[1]{\textcolor{blue}{#1}}
%\newcommand*{\groen}[1]{\textcolor{green}{#1}}
\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
\newcommand{\scripty}[1]{\ensuremath{\mathcalligra{#1}}}

% code for custom comments
\usepackage{tikz}
\usepackage{xcolor}
% markers (black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, magenta, olive, orange, pink, purple, red, teal, violet, white, yellow, more: https://en.wikibooks.org/wiki/LaTeX/Colors)
\newcommand{\marker}[3]{
  \tikz[baseline=(X.base)]{
    \node [fill=#1!40,rounded corners] (X) {#2:};
  }
  {\color{#1!80!black}#3}
}
\newcommand{\khb}[1]{\marker{teal}{KHB}{#1}}  % Kathy Breen
\newcommand{\replyhead}{\textbf{Author Reply: }}

@@

\def\Who{Andrew L. Ferguson} % Your name
\def\What{, PhD} % Your title
\def\Where{Pritzker School of Molecular Engineering\\University of Chicago} % Your department/institution
\def\department{Pritzker School of Molecular Engineering}
\def\institution{University of Chicago}
\def\Address{5640 South Ellis Avenue} % Your address
\def\CityZip{Chicago, IL 60637} % Your city, zip code, country, etc
\def\Email{e:~\url{andrewferguson@uchicago.edu}} % Your email address
\def\TEL{p:~(773)~702-5950} % Your phone number
\def\URL{w:~\url{www.ferglab.com}} % Your URL
\def\titleone{Associate Professor\\ Deputy Dean for Equity, Diversity, and Inclusion}

@@

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
%\hspace*{\longindentation} % Move the signature right
%\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.0in
\includegraphics[width=0.2\textwidth]{signature_720}
%\vskip 0.65in % Whitespace between the signature text and your name
\\
\noindent
\fromsig
\vskip -0.05in
\titleone\\
\department\\
\institution\\
%\vskip -0.1in
%\noindent cc: M.S.~Jones, B.~Ashwood, A.~Tokmakoff
}

@@

% what we did in this paper
\textbf{Key Results.}  In this work, we establish new understanding of the sequence-dependent hybridization/dehybridization kinetics and mechanism within a family of self-complementary pairs of 10-mer DNA oligomers by integrating coarse-grained molecular simulation, machine learning, data-driven inference of long-time kinetic models, and experimental temperature-jump infrared spectroscopy. We conducted more than 1 ms of coarse-grained molecular dynamics simulations and employed deep learning techniques to construct high-resolution Markov state models as predictive and interpretable models of the sequence-dependent dynamics. Our results reveal that the specific placement of interrupting G:C pairs within an otherwise repetitive AT sequence can have a profound impact on the kinetic pathways and mechanisms for association and dissociation of the DNA duplex.

@@

% fit for the journal
\textbf{Scope.}  This work fits within the scope of \textit{The Journal of the American Chemical Society} in that it reports new fundamental physical chemical understanding of the molecular pathways and mechanisms of sequence-dependent DNA hybridization/dehybridization. These sequence-dependent mechanisms are of both fundamental interest in biophysical and biochemical processes and of increasing importance in burgeoning DNA nanotechnology applications reliant on quantitative understanding of the sequence-dependent kinetic pathways and rates.

@@
